---
title: "Statistical Inference Method"
author: "Hoai Huong"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HOUSEKEEPING

```{r}
##### SETUP ##############################################################
# setwd("<your_path_here>")
rm(list = ls()) # Clear R's memory
options(stringsAsFactors=FALSE)# Make sure words are read in as characters rather than factors

##### IMPORT LIBRARIES ###################################################
library(ggplot2) # Visualization
library(stats) # Transformation
library(dplyr)
```

## IMPORT DATA

We choose the parameters to be Slope by Time because it can capture both the dexterity and speed of the drawing.

```{r}
##### GET FILENAMES ######################################################
Quantify <- list.files("Data", pattern = NULL, all.files = TRUE, full.names = FALSE)
Quantify <- Quantify[3:338] # Remove the first two garbage names
Quantify <- Quantify[!is.na(Quantify)]

##### GET DATA ############################################################
quantify_plotting <- data.frame(matrix(data=NA, nrow = 0, ncol = 8))  # Create empty data frames -- Prepare to store data
for(i in 1:length(Quantify)) {
  if(grepl("Slopedata", Quantify[i]) == TRUE) {
    dataframe <- read.csv(paste("Data/", Quantify[i], sep = ""))
    quantify_plotting <- rbind(quantify_plotting, dataframe)
    assign(Quantify[i], dataframe)
  }
}
quantify_plotting <- quantify_plotting[which(!is.na(quantify_plotting$slope)),]
quantify_plotting <- quantify_plotting[!is.infinite(quantify_plotting$slope),]
quantify_plotting$byDominant[which(quantify_plotting$byDominant == "TRUE")] <- "Dominant"
quantify_plotting$byDominant[which(quantify_plotting$byDominant == "FALSE")] <- "Non-Dominant"
```

## DATA VISUALIZATION

```{r}
plotting <- ggplot(data = quantify_plotting, aes(x = relativeTime, y = slope, group = interaction(timeUpload, userID), color = byDominant))+
  geom_line(alpha = 0.3)+
  geom_point(alpha = 0)+
  scale_colour_manual(values = c("#000000", "#00CCC6"))+
  facet_wrap(~byDominant, ncol = 1)+
  ##facet_grid(rows = vars(timeUpload),cols = vars(byDominant))+
  labs(title = "Slope by Time")+
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA),
        plot.margin = unit(c(1,1,1,1), units = , "cm"),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 11, face = "plain"),
        plot.title = element_text(size = 11 , hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(size = 11 , hjust = 0, face = "bold"),
        legend.title = element_blank(),
        legend.text = element_text(size = 11, face = "italic"),
        legend.position = "bottom",
        strip.text = element_text(size = 11, face = "bold"))

plotting
```

## DATA MODELLING

```{r}
##### CONVERSION ############################################################
convert.fft <- function(cs, sample.rate=1) { # Supporting Function
  cs <- cs / length(cs) # normalize
  
  distance.center <- function(c)signif( Mod(c),        4)
  angle           <- function(c)signif( 180*Arg(c)/pi, 3)
  
  df <- data.frame(cycle    = 0:(length(cs)-1),
                   freq     = 0:(length(cs)-1) * sample.rate / length(cs),
                   strength = sapply(cs, distance.center),
                   delay    = sapply(cs, angle))
  df
}
##### FOURIER TRANSFORMATION ################################################
quantify_plotting <- data.frame(matrix(data=NA, nrow = 0, ncol = 8))
fourier_plotting <- data.frame(matrix(data=NA, nrow = 0, ncol = 6))
for(i in 1:length(Quantify)) {
  if(grepl("Slopedata", Quantify[i]) == TRUE) {
    dataframe <- read.csv(paste("Data/", Quantify[i], sep = ""))
    dataframe <- dataframe[which(!is.na(dataframe$slope)),]
    dataframe <- dataframe[!is.infinite(dataframe$slope),]
    dataframe$fourier <- fft(dataframe$slope) # Fourier Transformation
    quantify_plotting <- rbind(quantify_plotting, dataframe)
    fourier_info <- convert.fft(dataframe$fourier) # Conversion
    fourier_info$label <- dataframe$byDominant
    fourier_info$ID <- paste(dataframe$userID, dataframe$timeUpload, sep = "_")
    fourier_plotting <- rbind(fourier_plotting, fourier_info)
    assign(Quantify[i], dataframe)
  }
}
quantify_plotting$byDominant[which(quantify_plotting$byDominant == "TRUE")] <- "Dominant"
quantify_plotting$byDominant[which(quantify_plotting$byDominant == "FALSE")] <- "Non-Dominant"
fourier_plotting$label[which(fourier_plotting$label == "TRUE")] <- "Dominant"
fourier_plotting$label[which(fourier_plotting$label == "FALSE")] <- "Non-Dominant"

```

## OBSERVATION

No distinct differences among all parameters, except for strength. Non-dominant tends to have cycles with greater strength.

```{r}
##### DELAY VS STRENGTH #####################################################
plotting <- ggplot(data = fourier_plotting, aes(x = strength, y = delay, group = ID, color = label))+
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.3)+
  scale_colour_manual(values = c("#000000", "#00CCC6"))+
  facet_wrap(~label, ncol = 1)+
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA),
        plot.margin = unit(c(1,1,1,1), units = , "cm"),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 11, face = "plain"),
        plot.title = element_text(size = 11 , hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(size = 11 , hjust = 0, face = "bold"),
        legend.title = element_blank(),
        legend.text = element_text(size = 11, face = "italic"),
        legend.position = "bottom",
        strip.text = element_text(size = 11, face = "bold"))
plotting

##### FREQUENCY VS CYCLE ####################################################
plotting <- ggplot(data = fourier_plotting, aes(x = cycle, y = freq, group = ID, color = label))+
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.3)+
  scale_colour_manual(values = c("#000000", "#00CCC6"))+
  facet_wrap(~label, ncol = 1)+
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA),
        plot.margin = unit(c(1,1,1,1), units = , "cm"),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 11, face = "plain"),
        plot.title = element_text(size = 11 , hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(size = 11 , hjust = 0, face = "bold"),
        legend.title = element_blank(),
        legend.text = element_text(size = 11, face = "italic"),
        legend.position = "bottom",
        strip.text = element_text(size = 11, face = "bold"))
plotting

##### STRENGTH VS CYCLE #####################################################
plotting <- ggplot(data = fourier_plotting, aes(x = cycle, y = strength, group = ID, color = label))+
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.3)+
  scale_colour_manual(values = c("#000000", "#00CCC6"))+
  facet_wrap(~label, ncol = 1)+
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA),
        plot.margin = unit(c(1,1,1,1), units = , "cm"),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 11, face = "plain"),
        plot.title = element_text(size = 11 , hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(size = 11 , hjust = 0, face = "bold"),
        legend.title = element_blank(),
        legend.text = element_text(size = 11, face = "italic"),
        legend.position = "bottom",
        strip.text = element_text(size = 11, face = "bold"))
plotting

##### DELAY VS CYCLE #########################################################
plotting <- ggplot(data = fourier_plotting, aes(x = cycle, y = delay, group = ID, color = label))+
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.3)+
  scale_colour_manual(values = c("#000000", "#00CCC6"))+
  facet_wrap(~label, ncol = 1)+
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA),
        plot.margin = unit(c(1,1,1,1), units = , "cm"),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 11, face = "plain"),
        plot.title = element_text(size = 11 , hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(size = 11 , hjust = 0, face = "bold"),
        legend.title = element_blank(),
        legend.text = element_text(size = 11, face = "italic"),
        legend.position = "bottom",
        strip.text = element_text(size = 11, face = "bold"))
plotting

##### STRENGTH VS FREQUENCY ###################################################
plotting <- ggplot(data = fourier_plotting, aes(x = freq, y = strength, group = ID, color = label))+
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.3)+
  scale_colour_manual(values = c("#000000", "#00CCC6"))+
  facet_wrap(~label, ncol = 1)+
  theme_classic()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA),
        plot.margin = unit(c(1,1,1,1), units = , "cm"),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 11, face = "plain"),
        plot.title = element_text(size = 11 , hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(size = 11 , hjust = 0, face = "bold"),
        legend.title = element_blank(),
        legend.text = element_text(size = 11, face = "italic"),
        legend.position = "bottom",
        strip.text = element_text(size = 11, face = "bold"))
plotting

```

## ASSESS THE MODELS

We classified the labels using strength:

```{r}
### Threshold strength = 0.8
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Non-Dominant")]))
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Non-Dominant" & fourier_plotting$strength >= 0.8)]))
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Dominant")]))
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Dominant" & fourier_plotting$strength >= 0.8)]))

### Threshold strength = 0.9
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Non-Dominant")]))
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Non-Dominant" & fourier_plotting$strength >= 0.9)]))
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Dominant")]))
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Dominant" & fourier_plotting$strength >= 0.9)]))

### Threshold strength = 1
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Non-Dominant")]))
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Non-Dominant" & fourier_plotting$strength >= 1)]))
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Dominant")]))
length(unique(fourier_plotting$ID[which(fourier_plotting$label == "Dominant" & fourier_plotting$strength >= 1)]))
```
